\section{Appendix}
\label{sec:appendix}

\subsection{Full Repositories List}
\label{sec:full_repo_list}
\input{document/full_repos}

\newpage
\subsection{Prompts in FeatBench}
\label{sec:prompts}
\begin{tcblisting}{
  colback=gray!5,
  colframe=black!50,
  fontupper=\ttfamily,
  title=Prompt for Feature-implementation PRs Identification,
  breakable,
  listing only,
  listing options={
    basicstyle=\ttfamily\small,
    breaklines=true,
    breakatwhitespace=true,
    breakindent=0pt,
  },
  skin=enhanced
}
Repository Context (README):
{readme}

---

Analyze the following software release notes and categorize the changes into: new_features, improvements, bug_fixes, and other_changes.
For each change, extract any PR references (like #123, PR456, pull #789, etc.) mentioned in the text.

Release version: {tag_name}
Release notes:{release_body}

Guidelines:
1. new_features: Brand new functionality, commands, rules, or capabilities
2. improvements: Enhancements to existing features, optimizations, performance improvements
3. bug_fixes: Bug fixes, error handling, crash fixes
4. other_changes: Documentation updates, dependency updates, refactoring (only if significant)
5. Extract PR numbers from various formats: #123, PR #456, pull 789, (#101), etc.
6. Only include PR numbers that are explicitly mentioned with the change
7. Ignore trivial changes like version bumps unless they're part of larger features
8. Use the repository context to better understand the project's domain and categorize changes more accurately

Return the result in JSON format:
{
    "new_features": [
        {
            "description": "Brief description of the new feature",
            "pr_ids": ["123", "456"]
        }
    ],
    "improvements": [
        {
            "description": "Brief description of the improvement", 
            "pr_ids": ["789"]
        }
    ],
    "bug_fixes": [
        {
            "description": "Brief description of the bug fix",
            "pr_ids": ["101"]
        }
    ],
    "other_changes": [
        {
            "description": "Brief description of other changes",
            "pr_ids": []
        }
    ]
}
\end{tcblisting}

\newpage
\begin{tcblisting}{
  colback=gray!5,
  colframe=black!50,
  fontupper=\ttfamily,
  title=Prompt for Uesr Requirement Synthesization,
  breakable,
  listing only,
  listing options={
    basicstyle=\ttfamily\small,
    breaklines=true,
    breakatwhitespace=true,
    breakindent=0pt,
  },
  skin=enhanced
}
You are creating a user requirement description that will be used to instruct another LLM to implement the exact same functionality. Your task is to analyze the PR information and code changes, then write a comprehensive user request that describes what the user wants to accomplish.

This description will be given to a coding LLM to generate the implementation, so you must ensure all functionality across all modified files is thoroughly described from the user's perspective.

Original Feature Description: {feature_description}

PR Title: {title}
PR Description: {body}

File Changes:
{files_text}

Your user requirement description must:
- Start with "I want to" and write as if a user is requesting this functionality from a developer
- Include ALL information from the original PR Description - do not omit any details, requirements, or context provided there
- Describe what the user wants to accomplish with complete detail for every file that was modified
- Include all functional requirements that would be needed to recreate this exact implementation
- When functions/methods have parameter changes (additions, deletions, modifications), describe what the user needs in terms of input data and configuration options, mentioning specific parameter names naturally within the context of the requirement
- Focus on the complete user workflow and all capabilities they need
- Describe the expected behavior and outcomes the user wants to achieve
- Ensure a coding LLM reading this could implement all the functionality without seeing the original code
- Write as a natural user request, not technical documentation
- Avoid phrases like "implement function X" or "modify file Y" - instead describe what the user wants to accomplish
- Do NOT include any actual code implementations, code snippets, or technical syntax - only describe the desired functionality and behavior from a user perspective
- Focus on WHAT the user wants to achieve, not HOW it should be implemented technically

Remember: This description will be the only guide for another LLM to recreate this functionality, so include every important detail about what the user wants to achieve, but express it as natural user requirements. You must incorporate all information from the original PR description. Never include code - only describe the desired outcomes and behaviors.
\end{tcblisting}

\newpage
\begin{tcblisting}{
  colback=gray!5,
  colframe=black!50,
  fontupper=\ttfamily,
  title=Prompt for Relevant Files Identification \& Python Version Detection,
  breakable,
  listing only,
  listing options={
    basicstyle=\ttfamily\small,
    breaklines=true,
    breakatwhitespace=true,
    breakindent=0pt,
  },
  skin=enhanced
}
Please analyze the project {repo_name} and perform two tasks:

TASK 1: List the most relevant files(no more than 20) for setting up a development environment, including:
0. CI/CD configuration files (such as .github/workflows/*.yml, .gitlab-ci.yml, .travis.yml, Jenkinsfile, etc.)
1. README files
2. Documentation files  
3. Installation guides
4. Development setup guides
5. Requirements and dependency files (requirements.txt, setup.py, pyproject.toml, Pipfile, etc.)
6. Configuration files (.python-version, .nvmrc, Dockerfile, docker-compose.yml, etc.)

Save the file list to a JSON file named "{setup_files}" in the project root directory.
Format the file list as a JSON array where each element is a string containing the relative path (relative to project root).
Example format: ["README.md", "requirements.txt", "setup.py", ".github/workflows/ci.yml"]

IMPORTANT: You MUST strictly save the file list using the exact filename "{setup_files}" as required. Do NOT use any other filename.

TASK 2: Analyze the configuration files you found and determine the most appropriate Python version for this project.
Based on your analysis, save the recommended Python version to a text file named "{version_file}" in the project root directory.
The file should contain ONLY the version number in the format "3.xx" (e.g., "3.8", "3.9", "3.10", "3.11").

IMPORTANT: You MUST strictly save the Python version using the exact filename "{version_file}" as required. Do NOT use any other filename.

If no specific version requirements are found, use "{default_version}" as the default.

IMPORTANT: The {version_file} file must contain ONLY the version number, no comments, no explanations, no additional text.

Focus only on identifying files and determining the Python version. Do not attempt to configure the environment yet.
\end{tcblisting}

\newpage
\begin{tcblisting}{
  colback=gray!5,
  colframe=black!50,
  fontupper=\ttfamily,
  title=Prompt for Configuration Agent,
  breakable,
  listing only,
  listing options={
    basicstyle=\ttfamily\small,
    breaklines=true,
    breakatwhitespace=true,
    breakindent=0pt,
  },
  skin=enhanced
}
Please help me configure the runtime environment for this project.
The project is {repo_name}.

MANDATORY FIRST STEP
First, read the **{setup_files}** file in the project root to understand which configuration files are available.
DO NOT PROCEED WITHOUT READING THIS FILE FIRST!
Then analyze these files to understand the project structure, dependencies, and requirements.

TEST REQUIREMENTS
You need to verify if it can successfully run the tests of the project.
You can tolerate a few test cases failures-as long as most tests pass, it's good enough.
Your test command must output detailed pass/fail status for each test item. This is mandatory. For example, with pytest, use the -rA option to get output like:
PASSED tests/test_resources.py::test_fetch_centromeres
PASSED tests/test_vis.py::test_to_ucsc_colorstring

**IMPORTANT:** Always use '--tb=short' to avoid excessive traceback output. Before running any tests, you MUST attempt to install 'pytest-timeout' and 'pytest-xdist', and ALWAYS add '--timeout=5' and '-n auto' to your pytest command to prevent any single test case from running too long and to speed up testing by running tests in parallel.

**IMPORTANT:** You must additionally test {test_files}. If these specific tests fail due to ImportError or ModuleNotFound, you should make every effort to install all optional dependencies. For other test files, you may tolerate ImportError or ModuleNotFound errors.

PYTHON VERSION INFORMATION
**IMPORTANT: About Python versions in this container:**
- The container has been pre-configured with the optimal Python version for this specific project 
- **IMPORTANT** The Python version specified in the {version_file} is already installed in the system. You can use 'python3.x' to run the project directly (e.g., python3.11)
- DO NOT attempt to install or change Python versions - the correct version is already installed in the system

PREFERRED INSTALLATION METHOD
- Always check which Python environment you're targeting before installation

**PRIORITY 1: Try using UV or poetry first (recommended)**
- Use 'uv' for dependency management and installation when possible
- For projects with pyproject.toml: try 'uv sync' or 'uv install'
- For projects with requirements.txt: try 'uv pip install -r requirements.txt'
- For editable installation: try 'uv pip install -e .'
- For running tests: try 'uv run pytest' or similar commands
- **IMPORTANT**: If you use uv to install dependencies, you MUST add the --exclude-newer {created_time} argument, for example: 'uv pip install -r requirements.txt --exclude-newer {created_time}'
- **IMPORTANT**: Ensure uv is using the system Python, not the agent's Python environment

**PRIORITY 2: Fallback to traditional tools if UV fails**
- If UV doesn't work or encounters issues, fall back to pip3
- Use system pip3: check with 'which pip3' to verify location
- Install necessary dependencies using system pip3
- If the project needs to be installed as a package, use 'pip3 install -e .'
- If you use pip to install dependencies, since pip cannot specify a cutoff date, you may encounter dependency version conflicts. In such cases, you need to manually resolve the conflicts according to the project's timeline. The cut-off time is {created_time}.
- **IMPORTANT**: Verify you're using system pip3, not agent's pip

Set up the correct Python environment and ensure all required packages are installed so that the test files can run properly.
Focus on resolving any import errors, missing dependencies, or configuration issues.

IMPORTANT: 
1. This Docker container may have been used to configure environments for the same project before.
2. UV is already installed in the container and configured with Tsinghua mirror for faster downloads.
3. If you encounter any testing-related errors (such as 'collected 0 items', 'no tests found', 'skip', 'INTERNALERROR', 
'TypeError: could not get code object', or other pytest framework internal issues), please ignore these errors and focus 
on environment configuration instead. These errors may indicate that test files don't exist, don't contain valid tests, 
or are pytest framework internal issues. In such cases, abandon trying to fix specific test files and continue with 
dependency installation and environment configuration.
4. Install all dependencies to the system Python, not in any virtual environment.
5. This Docker container may have been used to configure environments for the same project before.
Please first check what packages are already installed in the system Python environment to avoid conflicts.
\end{tcblisting}

\newpage
\subsection{Detailed Data Instance Example}
\input{tabs/examples}