\documentclass{article} %
\usepackage{colm2024_conference} %

\usepackage{microtype}
\usepackage[hidelinks]{hyperref} %
\usepackage{url}
\usepackage{booktabs}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage[flushleft]{threeparttable}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{xcolor, colortbl}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{textcomp}  %
\usepackage{scalerel}  %
\usepackage{tipa}
\usepackage{pifont}
\usepackage[subtle]{savetrees}
\usepackage[most]{tcolorbox}
\usepackage{listings}
\usepackage{caption}
\usepackage[normalem]{ulem}


\colmfinalcopy
\begin{document}

\frenchspacing %


\definecolor{linkcolor}{HTML}{cc0000}
\input{macros}
\title{\tech{} \cat{}:\\
Demystifying LLM-based Software Engineering Agents}


\newcommand{\seperate}{{\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ }}
\newcommand{\sseparate}{{\ \ }}

\author{Chunqiu Steven Xia\textsuperscript{$*$} 
\sseparate
Yinlin Deng\thanks{Contributed equally with author ordering decided by \href{https://senseis.xmp.net/?Nigiri}{\textit{Nigiri}}.}
\sseparate
\sseparate
\
Soren Dunn
\seperate
Lingming Zhang
\\[\bigskipamount]
University of Illinois Urbana-Champaign{ }\uiuc{}
\\[\bigskipamount]
\texttt{\{chunqiu2, yinlind2, sorend2, lingming\}@illinois.edu}
}



\maketitle

\begin{abstract}
Recent advancements in large language models (\llm{s}) have significantly advanced the automation of software development tasks, including code synthesis, program repair, and test generation. 
More recently, researchers and industry practitioners have developed various autonomous \emph{\llm agents} to perform end-to-end software development tasks. 
These agents are equipped with the ability to use tools, run commands, observe feedback from the environment, and plan for future actions. 
However, the complexity of these agent-based approaches, together with the limited abilities of current \llm{s}, raises the following question: 
\emph{Do we really have to employ complex autonomous software agents?}
To attempt to answer this question, we build \tech{} -- an \emph{agentless} approach to automatically resolve software development {issues}.
Compared to the verbose and complex setup of agent-based approaches, \tech employs a simplistic three-phase process of localization, repair, and patch validation, without letting the \llm decide future actions or operate with complex tools. 
Our results on the popular \swebenchlite benchmark show that surprisingly the simplistic \tech is able to achieve both the highest performance (\totalsolveperc{}, \totalsolve{} correct fixes) and low cost (\averagedollarcost) compared with all existing open-source software agents!
In fact, \emph{\tech has already been adopted by OpenAI as the go-to approach to showcase the real-world coding performance of both GPT-4o and the new OpenAI o1 models}.
Furthermore, we manually classified the problems in \swebenchlite and found problems with exact ground truth patches or insufficient/misleading issue descriptions.
As such, we construct \swebenchlitefiltered{} by excluding such problematic {issues} to perform more rigorous evaluation and comparison. 
Our work highlights the currently overlooked potential of a simplistic, {cost-effective} technique in autonomous software development.
We hope \tech will help reset the baseline, starting point, and horizon for autonomous software agents, and inspire future work along this crucial direction. 
We have open-sourced \tech at: \textcolor{linkcolor}{\url{https://github.com/OpenAutoCoder/Agentless}}

\end{abstract}



\input{secs/intro}
\input{secs/related}
\input{secs/approach}
\input{secs/experimental}
\input{secs/eval}
\input{secs/study}
\input{secs/conclusion}

\bibliographystyle{ACM-Reference-Format}
\bibliography{reference}

\end{document}
