% !TEX root = ../main.tex
\section{Introduction}
\label{sec:introduction}

Software engineering organizations are under growing pressure to turn coding agents from research demonstrations into deployable engineering infrastructure.
The decision they face is not whether an agent can suggest code in an IDE, but whether it can produce a reviewable pull request for substantive feature work in a production codebase.
At Huawei, this question is operational: multiple stack-level teams---Kubernetes, the CANN compiler stack (CANN), the MindSpeed training framework, and \texttt{torch\_npu}---are deciding in 2026 whether to route portions of their feature backlog through coding agents.
The deployment decision turns on a concrete question: \emph{when an agent is given a feature specification and the corresponding repository, can it produce a candidate PR that a human reviewer would accept with at most light revision?}

\paragraph{Why existing benchmarks do not answer this question.}
Coding-agent benchmarks have made fast progress on bug-fix and short-task settings.
Industry-watched leaderboards report that the strongest agent configurations now resolve over 70\% of issues on SWE-bench Verified~\cite{jimenez2024swebench}, and many leaderboards exist for short, well-localized tasks.
But these tasks are predominantly bug repair: they target a small set of files identified in advance, often supply the failing test, and reward minimal local edits.
Feature implementation differs in kind, not degree.
A new feature requires the agent to identify the right architectural surface, modify several files in coordinated ways, add or update tests, respect repository-specific conventions, and produce a change set that integrates with parallel ongoing work.
Industry surveys (e.g.,\@~\cite{github2024survey}) confirm that feature work---rather than localized bug fixes---is the bottleneck developers most want help with.
The gap between bug-repair benchmark scores and merge-ready feature pull requests is therefore not just a question of model size; it is a question about whether today's agents can deliver value on the part of the workflow that matters most to engineering teams.

\paragraph{An industrial audit.}
We answer the deployment question directly by auditing four leading commercial coding agents on a curated 62-task feature-implementation benchmark.
The benchmark combines 12 \emph{Huawei industrial tasks} drawn from the codebases that the rollout would touch (Kubernetes, the CANN/\texttt{torch\_npu} accelerator stack, and MindSpeed) with 50 \emph{open-source feature tasks} from a curated extension we call CapBench, drawn from 15 production-grade open source projects (Kafka, CPython, Airflow, TensorFlow, Apache Spark, Postgres, ClickHouse, etc.).
Each task is paired with a \emph{long} prompt (a multi-paragraph design proposal that mirrors a real feature spec) and a \emph{short} prompt (a one-sentence ticket-style description), giving us $62\times2=124$ task instances per agent.
We evaluate four agents---Claude Code (Opus 4.6), OpenAI Codex (GPT-5.4), Cursor Composer-2, and OpenCode/GLM-5.1---producing $124\times4=496$ end-to-end agent runs.
Each run is independently scored on three production-relevant axes (functional correctness, completeness/coverage, and behavioral equivalence to the reference implementation) by an automated four-evaluator panel; the verdict is decided by 3-of-4 majority.
We treat the four agents not as four versions of the same model but as four \emph{harnesses}: each ships its own planning loop, tool integration, code-search retrieval, and verification logic, and our results suggest these harness choices account for a large share of the variation we observe across vendors (Section~\ref{sec:industrial-deployment}).

This setup gives us a clean answer to the question Huawei's deployment teams asked: \emph{can today's coding agents take over feature delivery for our internal codebases?}

\paragraph{Why the verdict can be trusted.}
Two design choices preempt the obvious objections to LLM-judged benchmarks. \emph{(i)~Human-rater calibration.} We blind-rated the 96 Huawei-internal runs with three senior reviewers and confirmed 92.7\% PASS/non-PASS agreement with the four-LLM judge panel; the panel is the stricter of the two, never crowning a human-rejected run as PASS. \emph{(ii)~Anti-leakage sanitization.} An early Codex run on a Kubernetes task surfaced its ground-truth diff via \texttt{git log}; we treated this as a first-class threat, rebased every benchmark repo to a parent commit with target commits unreachable, blocked network access to upstream remotes, and re-ran the affected configurations. The numbers we report are after this re-run. Both procedures are detailed in \S\ref{sec:study-design}.

\paragraph{Headline findings.} Three findings shape the deployment recommendation:

\begin{itemize}
\item \textbf{Aggregate verdict: 8 of 496 runs pass strict majority review (1.6\%).} Treating the four evaluators as a panel and requiring 3-of-4 PASS, only 8 runs reach production-equivalent quality. The remaining 488 runs are split across PARTIAL (194 runs, 39\%) and FAIL (294 runs, 59\%).
\item \textbf{Harness choices appear to influence outcomes as much as model choice.} The two stronger harnesses (Claude Code and Codex CLI) reach 2.4\% PASS each, while Cursor Agent and OpenCode CLI reach 0.8\% PASS each---a 3$\times$ spread on identical tasks and prompts. Because every agent couples a specific harness to a specific frontier model, we cannot isolate harness from model; the comparison is product-level. We treat this as evidence that planning loop, retrieval, file resolution, and edit verification carry weight comparable to model choice in this regime, not as a clean harness-vs-model ablation.
\item \textbf{Long-prompt advantage is asymmetric.} On long prompts (with full design context), the strong harnesses lift PASS rate from 0\% to 4.8\%; the weaker harnesses improve only to 1.6\%. Better specification helps strong harnesses ship; for weak harnesses, more context improves scores but rarely converts outputs into production-equivalent PRs.
\item \textbf{Kubernetes-class tasks are still out of reach.} All 4 harnesses produce 0/8 PASS on the four K-tasks (Kubernetes scheduler / kubelet feature work). Cross-cutting feature work in mature Go infrastructure remains the hardest deployment frontier we measured.
\item \textbf{Failures are heterogeneous, but many are harness-addressable.} The 488 non-PASS runs split into semantic/correctness failures (41.4\%), coverage gaps (26.2\%), behavioral/design mismatches (10.0\%), and borderline partials (22.3\%). The important deployment signal is not that every failure is mere incompleteness, but that a large recoverable slice involves stopping early, omitting tests or generated artifacts, or failing to wire cross-module changes.
\end{itemize}


\paragraph{Contributions.} This paper makes three industrial-deployment contributions.
\emph{(1) Industrial audit protocol.} An audit protocol for feature-PR readiness that combines a 62-task benchmark (12 Huawei production tasks plus 50 OSS CapBench tasks), a four-LLM judge panel with strict majority verdicts, a repository sanitisation procedure that survived an attempted ground-truth exfiltration, and a 96-run blind human calibration ($\kappa=0.43$, 92.7\% agreement on PASS/non-PASS).
\emph{(ii) Empirical capability boundary.} Across 496 runs we find that today's commercial coding agents reach merge-ready quality on at most 2.4\% of tasks; the entire Kubernetes track is 0/32; long-form specifications double the strongest harnesses' PASS rate but do not move the weaker ones; and the failure mass is dominated by semantic errors (41.4\%) rather than incomplete coverage---a result that contradicts the common assumption that better retrieval would close the deployment gap.
\emph{(iii) Deployment policy.} The audit drives a concrete rollout decision used by Huawei's deployment review: ship agents only on bounded operator-tier work behind multi-judge harness gates (scope/test/judge), keep cross-module platform work in human hands, and treat the long-form specification template plus the calibrated panel as required infrastructure rather than research artifacts.

