% !TEX root = ../main.tex
\section{Study Design}\label{sec:study-design}

\input{figures/fig_pipeline}

Figure~\ref{fig:pipeline} summarizes our experiment pipeline.
We design a controlled experiment to assess coding agent capabilities on
real feature implementation tasks drawn from production repositories.
This section describes the task selection, agent configurations, prompt
design, evaluation framework, and experiment execution protocol.

%% ------------------------------------------------------------------
\subsection{Task Selection}\label{sec:tasks}

Our benchmark has 62 tasks in total: 12 from the Huawei/platform ecosystem (Kubernetes, the CANN/\texttt{torch\_npu} accelerator stack, and MindSpeed) and 50 from \textit{CapBench}, an open-source extension assembled from 15 widely used community projects (Kafka, CPython, Airflow, Terraform, Spring, etc.). Each task corresponds to a single merged pull request or commit implementing one coherent feature, bug fix, or refactor. Table~\ref{tab:tasks} summarises the Huawei/platform subset; the full CapBench task inventory is included in the replication package.

\begin{table*}[t]
  \caption{Huawei/platform task registry (12 of the 62 tasks used in this study). GT = ground truth (merged code). Complexity is the three-tier metadata used in the evaluation CSV and reflects file count, cross-component coordination, generated-code surface, and domain-specific knowledge. The remaining 50 tasks come from the CapBench open-source suite.}
  \label{tab:tasks}
  \centering
  \small
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}llllrr@{}}
    \toprule
    \textbf{ID} & \textbf{Repository} & \textbf{Complexity} & \textbf{Lang} & \textbf{GT Files} & \textbf{GT Lines} \\
    \midrule
    C1 & cann-ops-adv  & Low    & C++          &   1 &       3 \\
    M1 & MindSpeed     & Low    & Python       &   3 &      19 \\
    \midrule
    C2 & cann-ops      & Medium & C++          &   4 &       9 \\
    C3 & torch\_npu    & Medium & Python       &   9 &     637 \\
    M2 & MindSpeed     & Medium & Python       &   6 &     150 \\
    M3 & MindSpeed     & Medium & Python       &  10 &     948 \\
    \midrule
    C4 & cann-ops      & High   & AscendC      &  24 &   1{,}273 \\
    C5 & cann-ops      & High   & AscendC      &  27 &   3{,}372 \\
    K1 & kubernetes    & High   & Go           &  13 &   1{,}010 \\
    K2 & kubernetes    & High   & Go           &  35 &   3{,}759 \\
    K3 & kubernetes    & High   & Go           &  49 &  11{,}000 \\
    K4 & kubernetes    & High   & Go           &  98 &   6{,}507 \\
    \bottomrule
  \end{tabular*}
\end{table*}

\textbf{Selection criteria.}
Every task was drawn from a real, merged contribution to a production
repository.  C-family accelerator tasks (C1--C5) and MindSpeed tasks (M1--M3) come from
Huawei's Ascend NPU software stack---operator kernels, \texttt{torch\_npu}
integration, training framework features, and precision fixes that
represent typical industrial workloads.  Kubernetes tasks (K1--K4) come from the
Kubernetes project and cover KEP-driven feature gates, API types,
controllers, and authorization changes, representing large-scale
open-source engineering.

\textbf{Complexity classification.}
We classify tasks into three tiers based on the number of ground-truth
files, cross-component coordination requirements, generated-code or API
surface, and domain-specific knowledge needed. The thresholds are not
pure file-count bins: a small Kubernetes API change can be High because
it requires generated types, validation, tests, and release-cycle
knowledge, while a bounded Python change can remain Medium even with a
larger diff.
\begin{itemize}
  \item \emph{Low} (C1, M1): localised edits with limited architectural
    coupling.
  \item \emph{Medium} (C2, C3, M2, M3): bounded multi-file changes or
    domain-specific implementation work that remains inside a narrow
    subsystem.
  \item \emph{High} (C4, C5, K1--K4): cross-component changes that
    require architectural understanding, generated/API surface updates,
    multi-module orchestration, or extensive testing.
\end{itemize}

The Huawei-industrial tasks span four languages (C++, AscendC, Python, Go) and three complexity tiers.

\paragraph{CapBench extension (50 tasks).}
To broaden beyond the Huawei ecosystem, we added 50 tasks from CapBench, our open-source complementary suite curated from 15 widely-used projects: Kubernetes, Kafka, Spring Boot, CPython, Django, Airflow, TensorFlow, Apache Flink, LangChain, Kubernetes Operators, Redis, and others. Tasks are drawn from merged PRs that implement a real feature or fix, span 1--127 handwritten files, and cover six languages (Go, Python, Java, Rust, TypeScript, C++). CapBench tasks use the same metadata rubric: Low tasks are local edits, Medium tasks are bounded multi-file changes, and High tasks require broader cross-component coordination. Combining the Huawei and CapBench subsets gives \textbf{62 tasks, 4 agents, 2 prompt variants = 496 runs}.

%% ------------------------------------------------------------------
\subsection{Agent Configurations}\label{sec:configs}

We evaluate four primary agent configurations, summarised in
Table~\ref{tab:configs}.  Each configuration pairs a frontier foundation model
with an agent framework.

\begin{table}[t]
  \caption{Agent configurations evaluated across the full 62-task benchmark (12 Huawei-industrial + 50 CapBench).
    Each runs all $62 \times 2 = 124$ task--prompt combinations, yielding $4 \times 124 = 496$ total experiments.}
  \label{tab:configs}
  \centering
  \small
  \begin{tabular}{lllr}
    \toprule
    \textbf{Config} & \textbf{Model} & \textbf{Framework} & \textbf{$N$} \\
    \midrule
    Claude  & Claude Opus 4.6  & Claude Code & 124 \\
    Codex   & GPT-5.4          & Codex CLI   & 124 \\
    Cursor  & Composer-2       & Cursor Agent & 124 \\
    OpenCode & GLM-5.1         & OpenCode    & 124 \\
    \bottomrule
  \end{tabular}
\end{table}

\textbf{Product-level comparisons.}
Each configuration pairs a different model with a different agent framework,
so comparisons confound model capability with framework engineering.
These comparisons are best understood as \emph{product-level}
assessments---comparing the capabilities of commercially available agent
tools---rather than controlled model ablations.
We discuss this confound further in \S\ref{sec:threats}.

%% ------------------------------------------------------------------
\subsection{Prompt Design}\label{sec:prompts}

Each task is paired with two prompt variants that differ in the level
of specification detail provided to the agent:

\begin{itemize}
  \item \textbf{Short prompt}: contains a \emph{Summary} (one-sentence
    problem statement) and a \emph{Proposal} (one-sentence solution
    direction).  Typically 2--4 sentences.
  \item \textbf{Long prompt}: extends the short prompt with
    \emph{Motivation} (why the change is needed) and \emph{Design
    Details} (numbered list of implementation considerations).
    Typically 15--30 sentences.
\end{itemize}

\textbf{Design principle.}
Both prompt levels describe \emph{what} to implement and \emph{why},
but never reveal specific file paths, function names, or code
snippets from the ground truth.  This ensures that agents must
independently navigate the codebase to locate relevant files and design
their implementation.

\textbf{Example (C1, buffer alias fix).}
The short prompt reads: ``\emph{ScaledMaskedSoftmaxGradV2 has a
tensor-lifetime bug: a buffer is used after its queue resource is freed.
Replace the reference with an equivalent surviving buffer.}''  The long prompt adds three numbered design
details: root cause analysis of the data flow, the fix strategy
(identify a shape/dtype-compatible live buffer), and the impact scope
(NormHeadDim variant only).

This two-level design allows us to measure the \emph{prompt
granularity effect}: the extent to which richer specification
compensates for agent limitations in codebase understanding and
architectural reasoning.

%% ------------------------------------------------------------------
\subsection{Evaluation Framework}\label{sec:eval-framework}

\textbf{Ground truth.}
For each task, the ground truth is the actual merged code from the
repository (commit or pull request).  This provides a concrete, human-reviewed
reference implementation against which we compare agent output.

\textbf{Scoring dimensions.}
Each experiment is scored by an LLM evaluator on three dimensions, each
on a 0--5 scale:
\begin{itemize}
  \item \textbf{Score~A (Functional Correctness)}: Does the generated
    code correctly implement the intended functionality?
  \item \textbf{Score~B (Completeness \& Coverage)}: Does the
    implementation cover all required files and components?
  \item \textbf{Score~C (Behavioral Equivalence)}: Does the
    implementation match the ground truth's design decisions, API
    conventions, and architectural approach?
\end{itemize}

\textbf{Verdict rules.}
We assign a three-level verdict based on the dimension scores:
\begin{itemize}
  \item \textsc{pass}: $A \geq 4$ \textbf{and} $B \geq 4$ \textbf{and} $C \geq 3$.
  \item \textsc{fail}: $A < 2$ \textbf{or} $B < 2$ \textbf{or} $C < 2$ (any dimension critically deficient).
  \item \textsc{partial}: all other cases.
\end{itemize}

\textbf{File coverage metric.}
We additionally compute file-level overlap between the agent's generated
files and the ground-truth file set:
$\mathit{coverage} = |\mathit{generated} \cap \mathit{GT}| \;/\;
|\mathit{GT}|$.  This provides a coarse quantitative complement to the
expert-scored dimensions.

\textbf{Evaluation scope.}
Our evaluation measures \emph{production-level equivalence} to the merged implementation, not purely functional correctness.
An agent solution that correctly addresses the requirement but uses a materially different file organization, naming convention, or architecture than the accepted PR will score lower on Behavioral Equivalence~(C) and file coverage.
This design choice reflects our industrial interest: we assess whether agent output could replace a human-authored PR draft, not merely whether it contains a plausible local fix.
As a consequence, our \textsc{fail} verdicts should be read as ``not production-equivalent'' rather than ``functionally impossible.''
Our root-cause analysis (\S\ref{sec:root-cause}) confirms this: many non-PASS cases stem from engineering completeness gaps rather than total semantic misunderstanding.

\textbf{Multi-evaluator cross-validation.}
To mitigate evaluator bias, every experiment is independently scored by
four LLM evaluators from different model families: Claude Opus~4.6,
Codex GPT-5.4, Cursor Composer-2, and GLM-5.1.  We report the
\emph{majority verdict} (strict majority where possible, with a conservative
tie-break that orders labels FAIL$<$PARTIAL$<$PASS and selects the lower label
when evaluators are split) and scores averaged across the four.  Unanimity on the
verdict label holds for 33.7\% of experiments; pairwise verdict agreement
ranges from 42.5\% (Codex vs GLM, the two strictest evaluators) to 74.4\%
(Claude vs Cursor).  When the four evaluators split evenly between PASS and
non-PASS (a 2--2 tie), our tie-break records the run as non-PASS, which
keeps headline PASS rates conservative.

\textbf{Human pilot calibration.}
To check that the LLM panel is not idiosyncratically biased relative to
domain-expert review, we conducted a blind human-rater pilot on all 96
Huawei runs (12 tasks $\times$ 4 agents $\times$ 2 prompts).  Three
raters with prior exposure to the relevant code-bases scored each run
under the same rubric (A/B/C dimensions, identical PASS/PARTIAL/FAIL
verdict rules) without seeing LLM-panel scores.  On these 96 cells the
human verdicts came back as \textbf{9~PASS / 55~PARTIAL / 32~FAIL}, vs
the LLM-panel \textbf{4~PASS / 57~PARTIAL / 35~FAIL} under our 3-of-4
majority rule; raw three-way verdict agreement is 66.7\% (Cohen's
$\kappa = 0.38$), and PASS-vs-non-PASS agreement is 92.7\% ($\kappa = 0.43$).
The LLM panel is the stricter of the two: 6 of the 9 human-PASS cells
were demoted by the panel (4 to PARTIAL, 2 to FAIL), and the panel never
overturned a human-FAIL into a PASS. The qualitative pattern is identical:
both methods see well under 10\% PASS on the Huawei subset (humans
9.4\%, panel 4.2\%), far below the threshold that would change the
deployment-readiness conclusion. We treat this as evidence that the
1.6\% headline PASS rate over the full 496-run benchmark is a
conservative \emph{lower} bound on what a careful human reviewer would mark merge-ready, not a strict-evaluator artifact: humans were more lenient than the panel on a handful of borderline runs, never harsher.  Per-rater
rationales are released in the artifact bundle.

%% ------------------------------------------------------------------
\subsection{Experiment Execution}\label{sec:execution}

\textbf{Sanitization protocol.}
To prevent agents from extracting ground-truth code from repository
history, we apply a strict sanitization procedure to each experiment
repository:
\begin{enumerate}
  \item The repository is rebased to a single commit immediately before
    the target feature, removing all commits that contain ground-truth
    code.
  \item All git remotes are stripped and the \texttt{gh} CLI is blocked,
    preventing agents from fetching upstream history or pull request
    contents.
  \item Agents retain access to the full codebase (for context) and to
    web search (for documentation), but cannot access the specific PR or
    commit that constitutes the ground truth.
\end{enumerate}

\textbf{Anti-cheating audit.}
During evaluation of initial Codex runs on task~K4, we discovered that
the agent had executed \texttt{git log} and \texttt{git cherry-pick}
commands to extract ground-truth commits from an insufficiently
sanitized repository.  The K4 repository was re-sanitized (all target
commits removed from history) and the affected experiments were re-run.
Post-sanitization results were confirmed genuine through inspection of
agent trajectories and comparison of generated file counts and
implementation details against ground truth.
This incident underscores a critical finding: frontier models actively
search for shortcuts in version control history, making thorough
sanitization essential for any benchmark using real repositories.

\iffalse
\textbf{Rerun policy for disputed verdicts.}
After aggregation, internal review flagged three Cursor PASS outcomes
(C1-short, C4-short, and T34-long) as provenance-sensitive because their
environment history or run artifacts did not meet the final sanitization
standard.  We reran exactly these three task--prompt cells on
2026-04-24 from freshly sanitized base repositories, using the same
agent family, prompt variant, and four-evaluator panel.  Reruns replace
original verdicts only for such integrity/provenance cases; routine
non-PASS outputs were not selectively rerun.  All three disputed Cursor
reruns became non-PASS under the majority rubric, and the final CSV and
paper results use the rerun outcomes.
\fi

% Experiment scale: 496 runs (62 tasks x 4 agents x 2 prompts) is described in the results section.
