% !TEX root = ../main.tex
\section{Threats to Validity}
\label{sec:threats}

\subsection{Internal Validity}

Each task--agent--prompt cell was run once. Stochastic decoding and tool-use variation could move borderline outputs across verdict thresholds, so the reported SE-PASS rates are point estimates rather than tight confidence intervals. We mitigate this by reporting distributions, not only pass rates, and by emphasizing large effects such as 0/392 on non-trivially scoped main-corpus runs.

Each evaluated product combines a model, repository tools, planning loop, and validation behavior. We therefore interpret agent differences as product-level observations, not controlled model-vs-harness causal claims. Anti-leakage controls are another internal concern: an early run recovered a target patch from repository history, after which we rebased tasks to parent commits, removed remotes, and shimmed fetch paths. All reported runs use the fixed protocol.

The calibration subset also introduces human-rater subjectivity. The reviewers used the same rubric and were blinded to agent identity, but they still brought domain expectations to the task. We use their ratings to calibrate the SE-PASS boundary, not to claim that the LLM panel reproduces all human review judgments. A larger calibration sample across more organizations would reduce this threat.

\subsection{Construct Validity}

SE-PASS is a strict-equivalence construct. It requires functional correctness, coverage, and behavioral alignment with the merged reference implementation. This is appropriate for asking whether an agent can replace a human-authored PR, but it can reject valid alternative implementations that a reviewer might accept. We therefore treat SE-PASS as a conservative lower bound and use RA-PASS as a future relaxed reviewer-acceptable construct.

LLM-as-judge evaluation may introduce scoring bias, disagreement, and same-family/self-preference bias~\cite{wataoka2024selfpreference}. We reduce this risk through four independent evaluators, conservative tie-breaking, leave-one-family-out analysis, and human calibration on the 12-task industrial subset. The 400 main-corpus runs are still scored by the LLM panel alone, so a stratified human re-rating would strengthen the transfer assumption.

Ground-truth equivalence is another construct threat. The merged PR is a high-quality reference because it passed upstream review, but it is not the only possible implementation. We partially address this by separating A, B, and C scores: an output can receive partial credit for functional correctness or coverage even when it diverges from the reference design. The binary SE-PASS label should therefore be read together with mean score and failure signatures.

\subsection{External Validity}

The main corpus is drawn from 15 open-source projects and the calibration subset from one industrial partner's technology stack. The benchmark intentionally stresses long-horizon, system-level feature work; it should not be read as representative of all programming tasks or all industrial repositories. The results may be less pessimistic for smaller bug fixes, test-only tasks, or interactive pair-programming workflows with frequent human feedback.

The agent versions are fixed to the versions available during the study. Coding agents evolve quickly, and future product releases may improve long-context reasoning, repository navigation, and validation. The benchmark and scoring artefacts are released to support re-running the study as agents change.

Finally, the industrial subset reflects one technology stack: accelerator operators, distributed training, and platform engineering. These domains are relevant to systems organizations but may not transfer to mobile apps, web CRUD services, or data-pipeline maintenance. The main claim is therefore scoped: current agents are not ready for autonomous industrial feature delivery in system-level settings of this kind.
