\section{Conclusion}
\label{sec:conclusion}

Across 496 experiments spanning 62 real feature-implementation tasks
and 4 state-of-the-art coding agents, we find that modern commercial
agents are \emph{not ready} to autonomously complete production-quality
feature work.  The best-performing configuration (GPT-5.4 / Codex)
passes only 3.2\% of tasks and never clears the High-complexity tier.
Two trends are consistent across the data:

\begin{itemize}
  \item \textbf{A complexity cliff.}  Pass rate collapses from 12.5\%
  on Low-complexity tasks to 0 on High-complexity tasks, with
  Kubernetes-class multi-module refactors (K-family, 0/16 PASS)
  acting as an absolute ceiling for every agent we tested.
  \item \textbf{Prompt leverage.}  The single largest observed
  improvement was achieved by lengthening the prompt: long prompts lifted
  PASS rate by up to 25.0 pp on a per-task basis, comparable in
  magnitude to the full gap between the weakest and strongest agent
  frameworks. Input-side engineering dominates model choice.
  \item \textbf{Cursor passes short prompts best.}  Among the
  four evaluated agents, only Cursor benefits from long prompts on a
  \emph{per-task} basis; long prompts otherwise degrade the other
  agents' outputs (0--8pp), driven by length-sensitive context
  dilution (cf. \S\ref{sec:longcontext}).
\end{itemize}

\paragraph{Practitioner takeaways.}
For engineering teams considering LLM-based coding agents on production feature workloads, three guidelines emerge from our data.
\emph{First}, invest in prompt engineering before model selection: a well-specified task at the \emph{long} level of detail closes more of the capability gap than swapping models.
\emph{Second}, route Low-complexity refactors and single-file edits to agents, but keep multi-module feature work (particularly Kubernetes-family or protobuf-touching changes) with human engineers until an explicit harness (§\ref{sec:harness}) is in place.
\emph{Third}, the 42.7\% Codex-vs-GLM pairwise evaluator agreement implies that single-judge acceptance gates will mis-verdict at scale; any production adoption should ensemble at least three independent LLM judges with a conservative tie-break.

\paragraph{Future work.}
Our results motivate a research agenda centered on \emph{harness engineering}:
pre-edit planning, post-edit verification, and cross-file dependency tracing
as first-class components of an agent's loop rather than post-hoc shims. Section~\ref{sec:harness} presents a concrete roadmap drawing on the engineering-addressable failure share measured in this paper.
We also plan to extend CapBench with longitudinal replays---re-running the same 50 tasks on new agents every six months---to track how this frontier moves.
