Frontier coding agents now solve over 70\% of {SWE-bench} bug-fix tasks, prompting industry teams to ask whether they are ready to deliver \emph{feature pull requests}---multi-file, API-bearing, test-and-doc-bundled changes that engineers actually merge.
We frame each commercial agent as a \emph{harness}---a vendor-built wrapping of a frontier model with planning, retrieval, tool calls, and edit policies---and audit four of the leading harnesses today: Claude Code (Opus~4.6), Codex CLI (GPT-5.4), Cursor Agent (Composer-2), and OpenCode (GLM-5.1). The benchmark covers 62 feature-implementation tasks: 12 internal Huawei tasks (CANN, MindSpeed, torch\_npu, Kubernetes) and 50 open-source tasks from the CapBench suite (Kafka, CPython, Airflow, TiDB, Elasticsearch, and others).
Each agent is run with both short ($\sim$3-line) and long ($\sim$30-line) requirement prompts, producing $4\times62\times2=496$ runs.
Every run is scored independently by four LLM judges (Claude, Codex, Cursor, GLM) on a three-dimension rubric (functional correctness, completeness, behavioral equivalence) with majority-vote (3-of-4) adjudication.

The benchmark exposes a sharp \emph{feature-implementation gap}.
Only 8 of 496 runs reach a production-equivalent verdict (1.6\%); the strongest agents---Claude and Codex---each pass 2.4\% of their runs, Cursor and OpenCode pass under 1\%, and the per-pair evaluator agreement is 42--75\%.
The gap is concentrated, not noisy: every PASS comes from one of just four tasks (C1, C4, M1, T10), and the Kubernetes family yields 0\% PASS across 32 runs.
A long requirement prompt raises Claude/Codex from 0\% to 4.8\% PASS but does not rescue weaker agents.
On the engineering side, the dominant non-PASS failure mode is \emph{incomplete scope coverage}: agents understand the requirement but stop before touching all the files a real PR has to change.

Because the four agents share frontier-class backbone models but differ in scaffolding, the 4$\times$ spread between the best and worst PASS rate is fundamentally a \emph{harness-engineering} effect, not a model-capability effect. The interesting industrial design space is therefore not "which foundation model writes the best diff" but which harness elements---input scaffolding, output validation, scope enforcement, multi-evaluator gating---let a moderately strong agent ship feature pull requests reliably. We end with a four-step harness-engineering recipe (structured prompts, scope contracts, test-coverage gates, evaluator panels) that reframes our negative result as an actionable deployment lever: today's agents are not ready to ship features autonomously, but their failure modes are concrete enough to engineer around.
